Merging merges, more or less

### 2014-12-19 2015mergingmerges/section/01-Introduction.tex
ok

\subsection{Compile-Time Scheduling of Dynamic Constructs in Dataflow Program Graphs}
This is Ha and Lee\cite{ha1997compile}.

>>>>

\subsection{Compile-Time Scheduling of Dynamic Constructs in Dataflow Program Graphs}
This is Ha and Lee\cite{ha1997compile}.
``The main purpose of this paper is to show how we can define the profiles of dynamic constructs at compile-time''.

They use simulation or programmer pragmas to approximate the runtime statistics.
It looks like this is actually just about dynamic length/runtimes of certain nodes, rather than dynamic dependencies.
I don't think this is relevant.
